Fixing Vulnerabilities Potentially Hinders Maintainability

### 2020-08-13 paper/emse20.tex
esme update

>>>>

\section{Now}

\begin{itemize}
	\item How this is a problem or has an impact to the software project? What is the message to developers? 
	\item Implications: Discuss that depending on the project, maybe security is a first class citizen and should be fixed above all. Don't 
  just state that patch risk assessment should take maintainability into account. Saying that security should be a priority requires maybe a user study
  as evidence (check if the literature available is not enough).
  \item Review the secure programming languages implication. Check if the idea of fully secure exists. The idea to 
\end{itemize}

\section{Later}

\begin{itemize}
	\item 
\end{itemize}

\section{Not Sure}
\begin{itemize}
	\item I am not sure how the computer science curricula got mentioned from a motivation. I don't think vulnerabilities are been introduced, its 
 more that they get exposed. In this case, the implication does not make much sense from a practical point of view.
\end{itemize}
